---
title: "Introduction  to GreatSchoolsAPIProject"
author: "Samreen Nayyer-Qureshi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction  to GreatSchoolsAPIProject}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(GreatSchoolsAPIProject)
```

## Introduction
GreatSchools.org provides unparralleled information about a large number and variety of schools in the US. There are not many other sources that combine data from charter, public and private schools along with their ratings and demographic information the way GreatSchools does. 

GreatSchoolsAPIProject uses the Great Schools API's freemium access which is generally granted to individuals and insitutions with a basic GreatSchools.org account. The API Key requests must go through the GreatSchools's offices and are granted on a case by case basis. My Key is active and available until the end of the year 2019. 

There are ten data repositories available on GreatSchools API. A number of these API's cannot be accessed under the freemium access. Others offer information that is readily available and included in the Browse Schools and School Census Data reporsitories. For this reason, we will be accessing only these two subsets of the GreatSchools API. 

## Functions

The following four functions are included in the GreatSchoolsAPIProject

* `Browse.Schools()` - Access the GreatSchools API using parameters state, city and API Key to extract information about the schools that includes ratings, location and contact information, link to relevant webpages, etc.
* `Census.Data()` - Access the GreatSchools API using parameters df (a dataframe that contains a list of gsId) and API Key. The API endoint used in this function only accesses one school at a time. In order to build a data frame of multiple schools according to their location, we use the resulting dataset from `Browse.Schools()` to find gsID indeces and gather census data for the same schools.
* `Top.Rating()` - Accesses any dataset that tabulates schools ratings under `parentRating` or `gsRating` to find top 5 schools of a certain type. The types could be "charter", "private", or "public". 
* `School.Comp()` - Compiles the two datasets accessed via `Browse.Schools()` and `Census.Data()` in to one comprehensive dataframe without any duplicates. 


### `Browse.Schools()` Functionality and Output

Below is an example of how `Browse.Schools()` can be used to generate a list of schools within Oakland, CA. First 6 results are printed below. The parameter `Sys.getenv("GreatSchoolsAPI")` represents the API Key granted to me by GreatSChools.org

```{r}
Browse.Oakland<-Browse.Schools("CA", "Oakland",Sys.getenv("GreatSchoolsAPI"))
head(Browse.Oakland)
```

### `Census.Data()` Functionality and Output

Using the Browse.Oakland dataset, we can access the Census information of these schools using `Census.Data()`. The function would loop around all the provided school names to access census information. Notice that census information does not include gsId for all schools.

```{r}
Census.Oakland<-Census.Data(Browse.Oakland,Sys.getenv("GreatSchoolsAPI"))
head(Census.Oakland)
```


### `Top.Rating()` Functionality and Output

This function provides the top 5 schools of a certain "type" accrding to either parental rating or the Great SChools (gs) rating. The top 5 charter schools according to parent rating in Oakland are below.

```{r}
Top.Rating(Browse.Oakland,"charter","parent")
```

### `School.Comp()` Functionality and Output

This function can help to combine the School Search data and Census data into one comprehensve dataset. 

```{r}
Oakland.Schools<-School.Comp(Browse.Oakland,Census.Oakland)
head(Oakland.Schools)
```

## Datasets

Since three of the four functions included in this package depend on the data already acquired from the API, data exemplars are provided to aid with the exploratory exercises. 

### Browse.Schools.NY

This is the dataset created by running `Browse.Schools("NY", "Albany", Sys.getenv("GreatSchoolsAPI"))`. It includes records for 56 schools over 23 variables for Albany, NY. The docuentartion is provided in data.R.


### Census.Schools.NY

This is the ataset created by running `Census.Data(Browse.Schools.NY,Sys.getenv("GreatSchoolsAPI"))`. It includes records for 56 schools across 25 parameters. The documentation is provided in data1.R. 


