---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GreatSchoolsAPIProject

<!-- badges: start -->
<!-- badges: end -->

The goal of GreatSchoolsAPIProject is to access and extract information regarding schools based on state and city from GreatSchools.org's API. 

## Installation

You can install the released version of GreatSchoolsAPIProject from [GitHub](https://github.com/samreennq/GreatSchoolsAPIProject/tree/master/GreatSchoolsAPIProject) with:

``` r
# install.packages("devtools")
devtools::install_github("samreennq/GreatSchoolsAPIProject")
```
## Example

This is a basic example that shows how the GreatSchools API can be accessed using the `Browse.Schools()` function. More information is provided in the vignette. 

```{r example}
library(GreatSchoolsAPIProject)
Browse.Schools("NY", "Albany", Sys.getenv("GreatSchoolsAPI"))
```

